\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Mohammad Ahmad}} & \\
 LinkedIn: \href{https://www.linkedin.com/in/mahmad97}{linkedin.com/in/mahmad97} & Phone: +1--717--943--5417 \\
 GitHub: \href{https://github.com/mahmad97} {github.com/mahmad97} & Email: \href{mailto:mahmad97taha@gmail.com}{mahmad97taha@gmail.com}
\end{tabular*}


%-----------Education-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Computer Science}{Aug 2022 - May 2024}
	  {The Pennsylvania State University (Penn State), PA, USA}{}

	\resumeSubheading
      {Bachelor of Engineering in Computer Science}{Sep 2016 - Jun 2020}
      {The University of Hong Kong (HKU), Hong Kong}{Second Class Honors, First Division}
  \resumeSubHeadingListEnd

  
 %-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart
  	\resumeSubheading
      {\textbf{Teaching Assistant at Penn State}}{Sep 2022 - present}
      {Teaching, Mentoring, Grading}{}
    \resumeItemListStart
      \resumeItem{Teaching Assistant for courses ``CMPSC 101 Introduction to Programming", ``CMPSC 462 Data Structures", ``CMPSC 472 Operating System Concepts", and ``COMP 512 Advanced Operating Systems".}
    \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Engineer II at GOGOX}}{Sep 2020 - Jun 2022}
      {Full-stack Development, Front-end Development, Agile Methodologies, React.js, Next.js}{}
    \resumeItemListStart
      \resumeItem{Developed internal application to replace vendor-made legacy application. Reduced internal costs by 70\%.}
      \resumeItem{Coordinated with sprint team and product team as engineer-in-charge of the GogoBusiness web application.}
      \resumeItem{Added unit tests to improve code maintainability. Improved code coverage from 40\% to 75\%.}
      \resumeItem{Added reusable components to simplify larger components, improve code readability, and reduce code base size.}
      \resumeItem{Revamped the signup and order flows to reduce `flow abandonment'. Improved retention by 15\%.}
      \resumeItem{Revamped legacy portions of application to extend life, improve test coverage, and improve customer experience.}
      \resumeItem{Consolidated the design components used in the web applications to achieve uniform branding.}
      \resumeItem{Trained and mentored 3 summer interns.}
    \resumeItemListEnd
        
    \resumeSubheading
      {\textbf{Software Engineer Intern at Set Sail Software}}{May 2019 - Aug 2019}
      {Front-end Development, Vue.js}{}
    \resumeItemListStart
      \resumeItem{Removed the process of manual report-making by developing an on-demand and real time analytics dashboard.}
      \resumeItem{Aided product development life-cycle by implementing different kinds of user-behavior analytics.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Projects-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Vehicle Lane-change Prediction - Master's Project (Penn State)}{Dec 2023}
    {Machine Learning, Prediction System, Autonomous Driving, Sequence Classification}{}
    \resumeItemListStart
      \resumeItem{Developed a hybrid LSTM-HMM based model for vehicle lane-change prediction on the NGSIM dataset.}
      \resumeItem{Model outperformed baseline models based on LSTM and HMM techniques.}
      \resumeItem{Concluded that a such a hybrid model can improve performance for the lane-change prediction problem.}
    \resumeItemListEnd
    
    \resumeSubheading
    {AI Skincare Advisor - Final Year Project (HKU)}{Apr 2020}
    {Artificial Intelligence, Image Processing, Data Analysis, Machine Learning, Recommendation System}{}
    \resumeItemListStart
      \resumeItem{Developed a mobile application to conduct analysis on pictures and text to score skin problems using a pipeline of CV and ML algorithms.}
      \resumeItem{Application selects skincare products for the user from a database compiled using data from Sephora's website.}
      \resumeItem{The products are selected based on user's feature scores and text input using NLP and ML techniques.}
    \resumeItemListEnd
  
  \resumeSubheading
    {Web-based Chatting Application}{Nov 2017}
    {Full-stack Development, MEAN stack, Messaging System}{}
    \resumeItemListStart
      \resumeItem{Developed a chatting system which allows for multiple users sending messages simultaneously.}
      \resumeItem{Messages update automatically to allow real-time conversations.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
    

%-----------Skills-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item
    \textbf{Languages: }{(Expert) JavaScript/TypeScript, Python; (Others) Java, C/C++, C\#, Haskell, bash/shell}\\
    \textbf{Frameworks/Libraries: }{(Web) React.js, Redux, Next.js, Vue.js, Angular, Node.js, Express.js, Three.js; (ML) Python, Pytorch, Flask, Django; (Infrastructure) Linux, Git, Docker, Kubernetes; (Testing) Selenium, Cypress, Jest, React Testing Library; (Database) NoSQL, SQL, MongoDB, MySQL}\\
    \textbf{Technical Skills: }{Software Engineering, Full-stack and Front-end Development, AI/ML, OOP, Functional Programming, CI/CD, Data Structures, Algorithm Design, Problem Solving, Complexity Analysis, Formal Methods}\\
    \textbf{Other Skills: }{Agile Methodologies, Sprint Planning, Wind Surfing, Teaching and Mentoring}    
    }
 \end{itemize}


%-------------------------------------------
\end{document}
