\documentclass[a4paper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{multicol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
%----------HEADING----------
\textbf{{\Large Mohammad Ahmad}}
\vspace{5pt}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  Website: \href{https://mahmad.dev}{mahmad.dev} & Phone: 717-943-5417 \\
  Email: \href{mailto:mohammad.ahmad@utsa.edu}{mohammad.ahmad@utsa.edu} & Location: San Antonio, TX, USA \\
\end{tabular*}

%----------Summary----------
\section{Summary}
PhD student in Computer Science at UTSA advised by Dr. Mimi Xie, specializing in computer architecture, TinyML, and in-memory computing. Current research focuses on processing-in-memory architectures using domain wall memory. Experienced in full-stack AI engineering with a strong foundation in computer systems research.

%----------Research Interests----------
\section{Research Interests}
\setlength{\multicolsep}{-5pt}
\begin{multicols}{4}
  \begin{itemize}[leftmargin=0.3in, itemsep=2pt, parsep=0pt, topsep=2pt]
    \resumeItem{Computer architecture}
    \resumeItem{In-memory computing}
    \resumeItem{Domain wall memory}
    \resumeItem{TinyML}
    \resumeItem{ML on novel hardware}
    \resumeItem{IoT}
  \end{itemize}
\end{multicols}

%----------Education----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Doctor of Philosophy in Computer Science}{Jan 2025 - Present}
	    {The University of Texas at San Antonio (UTSA), TX, USA}{}
      \resumeItemListStart
        \resumeItem {Research focus: Processing-in-memory using domain wall racetrack memory.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Master of Science in Computer Science}{Aug 2022 - May 2024}
	    {The Pennsylvania State University (Penn State), PA, USA}{}
      \resumeItemListStart
        \resumeItem {Research focus: Hybrid LSTM-HMM based model for vehicle lane-change prediction.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Bachelor of Engineering in Computer Science}{Sep 2016 - Jun 2020}
	    {The University of Hong Kong (HKU), HK, HKSAR}{}
      \resumeItemListStart
        \resumeItem {Final year project: AI skincare advisor using ML-based skin problem scoring and product recommendation pipeline.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------Experience----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Graduate Research Assistant at ASIC Lab at UTSA}}{Jan 2025 - Present}
      {Research, Computer architecture, Computer systems, In-memory computing}{}
    \resumeItemListStart
      \resumeItem{Research \textbf{processing-in-memory architectures} using domain wall racetrack memory; designing and implementing algorithms and ML workloads on novel hardware and evaluating via simulations.}
      \resumeItem{Review literature across research interests; author and co-author \textbf{research papers}.}
    \resumeItemListEnd
    
  	\resumeSubheading
      {\textbf{Software Engineer at GoGoX}}{Sep 2020 - Jul 2022}
      {Full-stack Development, React.js, Next.js}{}
    \resumeItemListStart
      \resumeItem{\textbf{Developed in-house transport management system} to replace third-party legacy app, achieving \textbf{40\% regional cost reduction}, later scaled to other operating regions.}
      \resumeItem{\textbf{Revamped signup and order flows}, reducing \textbf{flow abandonment by 15\%} through fewer steps, updated branding, and reusable components.}
      \resumeItem{Consolidated design components for \textbf{uniform branding} across web applications and \textbf{improved test coverage from 40\% to 75\%}.}
      \resumeItem{Collaborated with product and design teams to ensure smooth delivery of software across multiple regions.}
    \resumeItemListEnd
        
    \resumeSubheading
      {\textbf{Software Engineer Intern at Set Sail Software}}{May 2019 - Aug 2019}
      {Front-end Development, Vue.js}{}
    \resumeItemListStart
      \resumeItem{Eliminated manual report-making by building an \textbf{on-demand, real-time analytics dashboard}.}
      \resumeItem{Supported the product development lifecycle by implementing \textbf{user-behavior analytics}.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------Teaching----------
% \resumeSubheading
%   {\textbf{Graduate Teaching Assistant at UTSA}}{Jan 2025 - Dec 2025}
%   {Teaching, Grading, MATLAB}{}
% \resumeItemListStart
%   \resumeItem{Course: Data Analysis and Visualization.}
%   \resumeItem{Graded assignments, labwork and tests, and helped prepare course content.}
% \resumeItemListEnd

% \resumeSubheading
%   {\textbf{Graduate Teaching Assistant at Penn State}}{Sep 2022 - May 2024}
%   {Teaching, Grading, C, Java, Python}{}
% \resumeItemListStart
%   \resumeItem{Course: Advanced Operating Systems, Operating Systems, Data Structures, Introduction to Programming.}
%   \resumeItem{Graded assignments and tests, and helped prepare course content.}
% \resumeItemListEnd

%----------Projects----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Vehicle Lane-change Prediction - Master's Project (Penn State) \; \href{https://github.com/mahmad97/Vehicle-Lane-Change-Prediction-using-LSTMHMM}{\underline{link}}}{Dec 2023}
    {Deep Learning, Prediction System, Autonomous Driving, Sequence Classification}{}
    \resumeItemListStart
      \resumeItem{Built a \textbf{hybrid LSTM-HMM model} for vehicle lane-change prediction on the NGSIM dataset, outperforming standalone LSTM and HMM baselines.}
    \resumeItemListEnd

    \resumeSubheading
    {Skin Infection Detection}{Apr 2023}
    {Deep Learning, Classification System, Android, Flask, Node.js, PostgreSQL, Docker}{}
    \resumeItemListStart
      \resumeItem{Built and deployed a \textbf{real-time skin infection detection app} with a full-stack distributed architecture (Android, Flask, Node.js, PostgreSQL, Docker).}
      \resumeItem{Enabled early diagnosis through on-device image classification, reducing reliance on in-person consultations.}
    \resumeItemListEnd

    \resumeSubheading
    {AI Skincare Advisor - Final Year Project (HKU) \; \href{https://github.com/mahmad97/AI_skincare_advisor}{\underline{link}}}{Apr 2020}
    {Artificial Intelligence, Image Processing, Data Analysis, Machine Learning, Recommendation System}{}
    \resumeItemListStart
      \resumeItem{Built a \textbf{CV and ML pipeline} to analyze user images and score skin problems, then recommend products from a Sephora-sourced database using NLP and ML techniques.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------Skills----------
\section{Skills}
\vspace{-2pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
  \item
  \textbf{Languages: }{Python, C/C++, JavaScript/TypeScript, Go, Java, bash/shell}\\
  \textbf{Frameworks/Libraries: }{React.js, Next.js, Node.js, Express.js, PyTorch, NumPy, Pandas, Flask, PostgreSQL}\\
  \textbf{Tools: }{LTSpice, Docker, Git, Linux}\\
  \textbf{Technical Skills: }{Computer Architecture, Processing-in-Memory, TinyML, AI/ML, Full-stack Development, System Design, CI/CD, RESTful APIs}
  }
\end{itemize}

\end{document}
